ICBEdataset figure Metro Maps

### 2022-02-04 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
refactored crisis maps

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icbe_metro_plots(x))

@@

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_sentence_tables(x))

@@

dyadic_mid <- read_csv(paste0(here::here(), "/data_other_datasets/mids/Dyadic MIDs 4.02/dyadic_mid_4.02.csv"))

@@

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) mids_metro_plots(x))

@@

icb_crises %>% filter(yrtrig>=1990) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))

@@

icb2v14 <- read_csv(here::here(), "/replication_paper/data/in/icb2v14.csv")

@@

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) icb_metro_plots(x))

@@

ged211 <- read_csv(here::here(), "/replication_paper/data/in/ucdp_ged/ged211.csv")

@@

icb_crises %>% filter(yrtrig>=1989) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/"), full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()

@@

icews_metro_plots <- function(crisis=426, topactor=F, exclude='', save_icews_file=NULL){

  print(crisis)
  #crisis=426
  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
  #save_icews_file = paste0(here::here(), "/replication_paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  if(is.null(savefile)){
    save_icews_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
  }

@@

  p_icews_metro_map  %>% saveRDS(save_icews_file)

@@

icb_crises %>% filter(yrtrig>=1995) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))

@@

phoenix <- bind_rows(a, b, c, d , e)

@@

                 left_join(CAMEO_eventcodes %>% dplyr::select(code=cameoeventcode     , cameo_event_label=eventdescription) ) %>%

                 left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameoeventcode, cameo_event_root_label=eventdescription) %>% filter(nchar(root_code)==2)) %>%

@@

codings_wide_agreed$crisno %>% unique() %>% sapply(FUN=function(x) phoenix_metro_plots(x))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

@@

      year=x17,
      month=x18,
      day=x19#,
      #random_text=x28
    ) %>% 
    filter(!is.na(src_country) & !is.na(target_country)) %>%
    distinct() %>% 
     mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
     left_join(CAMEO_eventcodes %>% mutate(cameoeventcode=cameoeventcode %>% as.numeric(cameoeventcode)) %>%
                 dplyr::select(cameo_code=cameoeventcode, cameo_label= eventdescription)  ) %>%
    mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
    distinct() %>%

@@

icb_crises %>% filter(yrtrig>=1977) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))

>>>>

c(196, 426) %>% sapply(FUN=function(x) icbe_metro_plots(x))

@@

c(196, 426) %>% sapply(FUN=function(x) icb_sentence_tables(x))

@@

dyadic_mid <- read_csv(paste0(here::here(), "/replication_paper/data/in/dyadic_mid_4.02.csv"))

@@

c(196, 426) %>% sapply(FUN=function(x) mids_metro_plots(x))

@@

icb_crises %>% filter(yrtrig>=1990 & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) mids_incidents_metro_plots(x))

@@

icb2v14 <- read_csv(paste0(here::here(), "/replication_paper/data/in/icb2v14.csv"))

@@

c(196, 426) %>% sapply(FUN=function(x) icb_metro_plots(x))

@@

ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged/ged211.csv"))

@@

icb_crises %>% filter(yrtrig>=1989 & crisno %in% c(196, 426) ) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) ucdp_ged_metro_plots(x))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"), full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()

@@

icews_metro_plots <- function(crisis=426, topactor=F, exclude='', savefile=NULL){

  print(crisis)
  #crisis=426
  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
  #save_icews_file = paste0(here::here(), "/replication_paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  if(is.null(savefile)){
    savefile <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
  }

@@

  p_icews_metro_map  %>% saveRDS(savefile)

@@

icb_crises %>% filter(yrtrig>=1995  & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) icews_metro_plots(x))

@@

phoenix <- bind_rows(a %>% mutate_all(as.character),
                     b %>% mutate_all(as.character),
                     c %>% mutate_all(as.character),
                     d %>% mutate_all(as.character) ,
                     e %>% mutate_all(as.character)
                     )

@@

                 left_join(CAMEO_eventcodes %>% dplyr::select(code=cameo_code     , cameo_event_label=cameo_label) ) %>%

                 left_join(CAMEO_eventcodes %>% dplyr::select(root_code=cameo_code, cameo_event_root_label=cameo_label) %>% filter(nchar(root_code)==2)) %>%

@@

c(196, 426) %>% sapply(FUN=function(x) phoenix_metro_plots(x))

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

@@

      year=x17,
      month=x18,
      day=x19#,
      #random_text=x28
    ) %>% 
    filter(!is.na(src_country) & !is.na(target_country)) %>%
    distinct() %>% 
     mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
     left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code %>% as.numeric()) %>%
                 dplyr::select(cameo_code=cameo_code, cameo_label= cameo_label)  ) %>%
    mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
    distinct() %>%

@@

icb_crises %>% filter(yrtrig>=1977 & crisno %in% c(196, 426)) %>% pull(crisno) %>% unique()  %>% sapply(FUN=function(x) terrier_metro_plots(x))
